---
title: "Assignment2.1-2017555012"
author: "Sümeyra Çam"
date: "21 01 2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
set.seed(2017555012)
library(knitr)


data<-read_csv("C:/Users/SÜMEYRA/Desktop/data/covid-data-2020.csv")

covid_data <- sample(1:nrow(data), 1000)
covid_data <- data[covid_data, ]


```

```{r echo=FALSE}
kable(covid_data %>% head(10))
```

## Q1: Calculate the five-number summary statistics of covid-19 daily new cases for each country within each month.

```{r echo=FALSE}
five_numbers<- covid_data %>%
  group_by(location,month) %>%
  summarize(min=min(new_cases),
            Q1=quantile(new_cases,probs=0.25,na.rm=TRUE),
            Q2=quantile(new_cases,0.50,na.rm=TRUE),
            Q3=quantile(new_cases,probs=0.75,na.rm=TRUE),
            max=max(new_cases))
```

```{r echo=FALSE}
kable(five_numbers %>% head(10))
```


## Q2: Find the highest daily cases and deaths separately for each country.

```{r echo=FALSE}
max_cases <- group_by(covid_data, location)
summarise(max_cases, 
          max_case = max(new_cases, na.rm=TRUE),
          max_death = max(new_deaths, na.rm=TRUE),.groups = 'drop')
```


## Q3: Identify the month in which the mean daily cases is the highest for each country.

```{r echo=FALSE}
highest_month <- covid_data %>%
    group_by(location,month) %>%
    summarize(Mean_cases = mean(new_cases),.groups = 'drop') %>%
    arrange(desc(Mean_cases)) 
```

```{r echo=FALSE}
kable(highest_month %>% head(10))
```

## Q4: Select 3 country and plot the distribution of daily cases by month.Use location as clusters (i.e., color=location) to show the difference between countries.

```{r include=FALSE}
selected_locations<-covid_data%>%
  group_by(month)%>%
  filter(location ==c("Russia","France","Bulgaria") )

x<-ggplot(selected_locations, aes(x=month, y= new_cases, color=location)) +  geom_point()


```

```{r final, echo=FALSE}
plot(x)
```

```