---
title: "Assignment1-2017555012"
author: "Sümeyra Çam"
date: "21 01 2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(knitr)
library(dplyr)
library(tidyverse)
library(starwarsdb)
```

## Q1: How many characters do have at least one starship?

```{r include=FALSE}

sw <- starwars
sw

have_starship <- sw %>%
  group_by(name) %>%
  summarize(num_starships = lengths(starships ),.groups = 'drop' ) %>%
  arrange(desc(num_starships)) %>%
  filter(num_starships >= 1) 
```

```{r echo=FALSE}
kable(count(have_starship))
kable(have_starship)
```



## Q2: Get the frequencies of the eye color of the characters

```{r include=FALSE}
eye_frequency <- sw %>%
  group_by(eye_color) %>%
  summarize(eye_color,.groups = 'drop' ) %>%
  count(eye_color) %>%
  arrange(desc(n))
```

## Ranked data:

```{r echo=FALSE}
kable(eye_frequency)
```

## Q3: According to the data available, what are the mean (average) age values across each species? Find the 3 oldest species.

```{r echo=FALSE}
mean_age<- sw %>%
  filter(!is.na(birth_year)) %>%
  filter(!is.na(species)) %>%
  group_by(species) %>%
  summarize(
    mean_birth=mean(birth_year)
  )
(mean_age)

species<-arrange(mean_age,desc(mean_birth))
species[c(1,2,3),] 


```


## Q4: A new data set by adding a new observation to this data

```{r echo=FALSE}
starwars_new <- sw %>% add_row(name = 'Sümeyra Çam',height = 164.0, mass = 80 ,hair_color = 'brown',skin_color = 'warm ivory',eye_color = 'brown',birth_year = 23,sex = 'female',gender = 'feminine', homeworld = 'Stewjon',species = 'Human',
                                  films = list('The Clone Wars'),vehicles = list('T-47 Airspeeder'),starships = list('Luxury 3000'))


kable(starwars_new%>%tail(1))

```

## Q5: Calculate the body mass index (BMI)

```{r echo=FALSE}
starwars_new<-starwars_new %>%
  mutate(starwars_new,bmi=mass/((height/100)^2))

starwars_new<-starwars_new %>%
  mutate(starwars_new,bmi_result=if_else(bmi < 18.5,"underweight",
                                        if_else((18.5 < bmi) & (bmi < 24.99),"healthy",
                                                if_else((25.0 < bmi) & (bmi < 29.99),"overweight",
                                                        "obese"))))

kable(starwars_new%>%head(1))

```

## Q6: Plot the distribution of ages less than 100 by BMI groups

```{r echo=FALSE}
starwars_new$birth_year<-as.integer(starwars_new$birth_year)

hundred_below<- starwars_new%>%
  na.omit(select(birth_year,bmi,bmi_result))%>%
  filter(birth_year<100.0)

```


```{r echo=FALSE}
ggplot(data = hundred_below, mapping = aes(x=bmi_result,y=birth_year))+
  geom_boxplot( color="blue", fill="blue",
                alpha=0.2,
                
                notch=FALSE,
                notchwidth = 0.8,
                
                outlier.colour="red",
                outlier.fill="red",
                outlier.size=3
  )

```

## Q7: By plotting a graph, show the relationship between age and BMI values.Re-plot the same graph after filtering the data as both age and BMI less than 100.

```{r echo=FALSE}
ggplot(data=starwars_new)+
  geom_point(mapping=aes(x=birth_year,y=bmi))+
  geom_smooth(mapping=aes(x=birth_year,y=bmi))
ggplot(data=hundred_below,mapping=aes(x=birth_year,y=bmi))+
  geom_point()+
  geom_smooth(data=filter(hundred_below,birth_year<100 & bmi<100))



```


