---
title: "Assignment3-2017555012"
author: "Sümeyra Çam"
date: "21 01 2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
set.seed(2017555012)
library(tidyverse)
library(stringr)
library(knitr)
```

## Q1: Write a function that finds a prime number(s) given a set of numbers. Your function also provides prime factors of non-prime numbers.

```{r echo=FALSE}
set_of_num<-sample(c(1:500), size=5, replace=TRUE)
set_of_num

is_prime <- function(numbers) {
  p_num<-c()
  n_num<-c()
  for(x in numbers){
    bool=TRUE
    k = 2
    while(k < (x/2)){
      if(x%%k == 0)
        bool=FALSE
      k <- k + 1
    }
    if(x == 2) bool=TRUE
    if(bool == TRUE){
      p_num<-c(p_num, x)
    }
    else if(bool == FALSE){
      n_num <- c(n_num, x)
    }
  }
  c = 1
  print("Non-Prime Numbers:")
  while(c <= length(n_num)){
    numvec <- n_num[c]
    for(num in numvec){
      if(num>2){
        numvec <- c()
        while(num %% 2 == 0){
          numvec <- c(numvec, 2)
          num <- num/2
        }
        i = 3
        while(num!=1){
          while(num%%i == 0){
            numvec <- c(numvec, i)
            num<-num/i
          }
          i<-i+2
        }
      }
      print(c(n_num[c],numvec))
      c <- c + 1
    }
  }
  print(list(c("Prime numbers:" ,p_num)))
}
```

```{r echo=FALSE}
kable(is_prime(set_of_num))
```

## Q2: Write a function that finds the letter numbers of all words in a given text and sorts the text according to those numbers from words with few letters to words with many letters. Sort the words containing the same number of letters alphabetically.

```{r echo=FALSE}
new_sentences <- sample(sentences, 6,)

df <- tibble(
  word = new_sentences,
  #i = seq_along(word)
)
head(df)

q2<-function(df){

  a <- df %>% select(word) %>% unlist(use.names = FALSE)
  string1 <- str_c(a,collapse=" ")
  string2 <- str_to_lower(string1, locale = "en")
  string3 <- strsplit(string2, " ")[[1]]
  string4 <- str_replace_all(strsplit(string2, " ")[[1]], "[\\.\\,\\;\\:\\?\\!]$", "")

  tibble_of_words <- tibble(
    words = factor(),
    frequency = numeric()
  )
 
  for(token in string4){
    flag <- sum(str_detect(string4,regex(token)))
    tibble_of_words <- tibble_of_words %>% add_row(words = token, frequency = flag)
    
  }
  tibble_of_words<-tibble_of_words %>%
    mutate(
      vowels = str_count(tibble_of_words$words,"[aeiou]"),
      consonants = str_count(tibble_of_words$words,"(?i)([b-z&&[^eiou]])"),
      length = vowels + consonants
    )
  
  tibble_of_words$words<-as.character(tibble_of_words$words)
  tibble_of_words <- arrange(tibble_of_words,length)
  tibble_of_words <- tibble_of_words[with(tibble_of_words, order(length,words)), ]
  
  return (str_c(tibble_of_words$words, collapse = " "))
}
```

```{r echo=FALSE}
kable(q2(df))
```
